<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
  )
options(width = 115)
```

# ExifTool functionality from R

The **exiftoolr** package provides a thin wrapper around a local
installation of ExifTool, giving users easy access to
[ExifTool][ExifTool-home] functionality from within R. The package can
be configured () to use an already existing ExifTool
installation. Alternatively, the utility function `install_exiftool()`
(run just once following package installation) can be used to download
and install the most up-to-date version of ExifTool into the
**exiftoolr** package directory.

A simple call to `exif_read()` will then read metadata from one or
more image or other files into a `data.frame` with one row per file
and one column per metadata field. The function `exif_call()` supports
more general calls to the underlying ExifTool utility (some examples
of which are displayed [here][ExifTool-examples]).


## What is ExifTool?

Phil Harvey's ExifTool is an excellent and comprehensive open source
utility for reading, writing and editing meta information in a wide
variety of files. As noted on the [project homepage][ExifTool-home]:

> ExifTool supports many different metadata formats including EXIF, GPS,
> IPTC, XMP, JFIF, GeoTIFF, ICC Profile, Photoshop IRB, FlashPix, AFCP
> and ID3, as well as the maker notes of many digital cameras by Canon,
> Casio, FLIR, FujiFilm, GE, HP, JVC/Victor, Kodak, Leaf,
> Minolta/Konica-Minolta, Motorola, Nikon, Nintendo, Olympus/Epson,
> Panasonic/Leica, Pentax/Asahi, Phase One, Reconyx, Ricoh, Samsung,
> Sanyo, Sigma/Foveon and Sony.



## ExifTool and Perl

ExifTool is written and primarily distributed as a Perl library which
can be used on any computer with a working Perl installation. Those
include most Linux and Mac machines, which typically have Perl
installed by default. Machines running Windows often do **not** have
Perl installed (though it may be easily installed using installers
distributed by [Strawberry Perl][Strawberry-Perl] or [Active State
Perl][ActiveState-Perl]).

Windows users without Perl do not, though, need to install Perl to
accesss ExifTool's functionality. They instead have the option of
installing stand-alone ExifTool compiled executable distributed on the
ExifTool home page. Like the Perl library, the Windows executable can
be downloaded using `exiftoolr::install_exiftool()`


## Installation and setup

To install **exiftoolr** from GitHub, do:

```{r, gh-installation, eval = FALSE}
devtools::install_github("JoshOBrien/exiftoolr")
```

Then, to install a copy of the ExifTool library or executable into the
**exiftoolr** package's directory tree, where calls to functions in
the **exiftoolr** package will automatically find it, run
`install_exiftool()`:

```{r, exiftool-installation, eval = FALSE}
exiftoolr::install_exiftool()
```

**exiftoolr** makes a reasonable attempt to find local copies of Perl
and ExifTool, and in most cases will need no hints to find them. For
situations in which you need more control over which Perl or Exiftool
is used, use the `configure_exiftool` and/or `configure_perl`
executables or, alternatively, set the `


## Usage

`exif_read()` will quickly read metadata from one or more image files,
returning the results in a plain `data.frame`: 

```{r, example}
library(exiftoolr)
image_files <- dir(system.file("images", package = "exiftoolr"), 
                   full.names = TRUE)
exifinfo <- exif_read(image_files)
dim(exifinfo)
names(exifinfo)[1:60] ## List the first 60 metadata fields read by ExifTool
```

As you can see, there are a lot of columns! To extract only those
tags that are actually needed, use the `tags` argument:

```{r}
exif_read(image_files, tags = c("filename", "imagesize"))
```

The `tags` argument also accepts simple regular expressions. For
instance, to extract all fields with names containing the substring
`"GPS"`, you could use the following call:

```{r}
exif_read(image_files[1], tags = "*GPS*")[,-1]
```


To access more general ExifTool functionality, you can use the
function `exif_call()` to roll your own call to ExifTool. For the
previous example, it would look something like this:

```{r}
exif_call(args = c("-n", "-j", "-q", "-filename", "-imagesize"),
          fnames = image_files)
```





[ExifTool-home]: http://www.sno.phy.queensu.ca/%7Ephil/exiftool/
[ExifTool-examples]: http://owl.phy.queensu.ca/~phil/exiftool/examples.html
[Strawberry-Perl]: http://www.strawberryperl.com/
[ActiveState-Perl]: https://www.activestate.com/activeperl/downloads
