<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
  )
options(width = 115)
```

# ExifTool functionality from R

The **exiftoolr** package provides a thin wrapper around a local
installation of [ExifTool][ExifTool-home], giving users easy access to
ExifTool functionality from within R. The package can be configured to
use an already existing ExifTool installation. Alternatively, the
utility function `install_exiftool()`, run just once following package
installation, can be used to download and install the most up-to-date
version of ExifTool into the **exiftoolr** package directory.

A simple call to `exif_read()` will then read metadata from one or
more image or other files into a `data.frame` with one column per
metadata field and one row per file. The function `exif_call()`
supports more general calls to the underlying ExifTool utility (some
examples of which are displayed [here][ExifTool-examples]).


## What is ExifTool?

Phil Harvey's ExifTool is an excellent and comprehensive open source
utility for reading, writing and editing meta information in a wide
variety of files. As noted on the [project homepage][ExifTool-home]:

> ExifTool supports many different metadata formats including EXIF, GPS,
> IPTC, XMP, JFIF, GeoTIFF, ICC Profile, Photoshop IRB, FlashPix, AFCP
> and ID3, as well as the maker notes of many digital cameras by Canon,
> Casio, FLIR, FujiFilm, GE, HP, JVC/Victor, Kodak, Leaf,
> Minolta/Konica-Minolta, Motorola, Nikon, Nintendo, Olympus/Epson,
> Panasonic/Leica, Pentax/Asahi, Phase One, Reconyx, Ricoh, Samsung,
> Sanyo, Sigma/Foveon and Sony.



## ExifTool and Perl

ExifTool is written and distributed as a Perl library. It can thus be
used "out of the box" on any computer that (like most Linux and Mac
machines) has a working Perl installation. Windows machines often do
**not** have Perl installed (though easy-to-use installers are
available from, e.g., [Strawberry Perl][Strawberry-Perl] and [Active
State Perl][ActiveState-Perl]).

Windows users do not, however, need to install Perl to accesss
ExifTool's functionality. They may instead install the standalone
ExifTool executable distributed on the ExifTool home page. Like the
Perl library, the Windows executable can be downloaded and installed
using the function `install_exiftool()`.


## Installation and setup

To install **exiftoolr** from GitHub, do:

```{r, gh-installation, eval = FALSE}
devtools::install_github("JoshOBrien/exiftoolr")
```

Then, to install a copy of the ExifTool library or executable into the
**exiftoolr** package's directory tree, where calls to functions in
the **exiftoolr** package will automatically find it, run
`install_exiftool()`:

```{r, exiftool-installation, eval = FALSE}
exiftoolr::install_exiftool()
```

**exiftoolr** makes a reasonable attempt to find local copies of Perl
and ExifTool, and in most cases will need no hints to find them. For
situations in which want more control over which Perl or ExifTool is
used, set their paths with either an explicit call to
`configure_exiftool()` or by setting the environment variables
`"ET_PERL_PATH"` and `"ET_EXIFTOOL_PATH"`.


## Usage

`exif_read()` will quickly read metadata from one or more image files,
returning the results in a plain `data.frame`: 

```{r, example}
library(exiftoolr)
image_files <- dir(system.file("images", package = "exiftoolr"), 
                   full.names = TRUE)
exifinfo <- exif_read(image_files)
dim(exifinfo)
names(exifinfo)[1:60] ## List the first 60 metadata fields read by ExifTool
```

As you can see, there are a lot of columns! To extract only those
tags that are actually needed, use the `tags` argument:

```{r}
exif_read(image_files, tags = c("filename", "imagesize"))
```

The `tags` argument also accepts simple regular expressions. For
instance, to extract all fields with names containing the substring
`"GPS"`, you could use the following call:

```{r}
exif_read(image_files[1], tags = "*GPS*")[,-1]
```


To access more general ExifTool functionality, you can use the
function `exif_call()` to roll your own call to ExifTool. For the
previous example, it would look something like this:

```{r}
exif_call(args = c("-n", "-j", "-q", "-filename", "-imagesize"),
          fnames = image_files)
```





[ExifTool-home]: http://www.sno.phy.queensu.ca/%7Ephil/exiftool/
[ExifTool-examples]: http://owl.phy.queensu.ca/~phil/exiftool/examples.html
[Strawberry-Perl]: http://www.strawberryperl.com/
[ActiveState-Perl]: https://www.activestate.com/activeperl/downloads
