```{r, echo=FALSE, include=FALSE, cache=FALSE}
require(knitr)
render_jekyll()
```

# EXIF Data in R

Ever needed to read in EXIF data from images or other files in R?
[ExifTool](http://www.sno.phy.queensu.ca/%7Ephil/exiftool/) by Phil
Harvey is the most comprenesive tool available for reading, writing
and editing meta information in a wide variety of files. ExifTool
supports many different metadata formats including EXIF, GPS, IPTC,
XMP, JFIF, GeoTIFF, ICC Profile, Photoshop IRB, FlashPix, AFCP and
ID3, as well as the maker notes of many digital cameras by Canon,
Casio, FLIR, FujiFilm, GE, HP, JVC/Victor, Kodak, Leaf,
Minolta/Konica-Minolta, Motorola, Nikon, Nintendo, Olympus/Epson,
Panasonic/Leica, Pentax/Asahi, Phase One, Reconyx, Ricoh, Samsung,
Sanyo, Sigma/Foveon and Sony.

`exiftoolr` provides a thin wrapper around ExifTool and allows one to
read image file metadata with a simple command:

```{r eval=FALSE}
library(exiftoolr)
read_exif("my_file.jpg")
```

## Installation

[ExifTool](http://www.sno.phy.queensu.ca/%7Ephil/exiftool/) is written
in Perl, so if you are on windows you need to install Perl before
installing exiftoolr (easily done from [Strawberry
Perl](http://www.strawberryperl.com/):
[64-Bit](http://strawberryperl.com/download/5.22.1.2/strawberry-perl-5.22.1.2-64bit.msi)
(most users),
[32-Bit](http://strawberryperl.com/download/5.22.1.2/strawberry-perl-5.22.1.2-32bit.msi)
(advanced)). Mac and linux users already have this installed. To
install the exiftoolr package, use the `devtools::install_github()`
command like this:

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("JoshOBrien/exiftoolr")
```
