```{r, echo=FALSE, include=FALSE, cache=FALSE}
require(knitr)
render_jekyll()
```

## Overview

Phil Harvey's [ExifTool][exiftool-home] is the most comprensive tool
available for reading, writing and editing the metadata contained in a
wide variety of files. ExifTool supports many different metadata
formats including EXIF, GPS, IPTC, XMP, JFIF, GeoTIFF, ICC Profile,
Photoshop IRB, FlashPix, AFCP and ID3, as well as the maker notes of
many digital cameras by Canon, Casio, FLIR, FujiFilm, GE, HP,
JVC/Victor, Kodak, Leaf, Minolta/Konica-Minolta, Motorola, Nikon,
Nintendo, Olympus/Epson, Panasonic/Leica, Pentax/Asahi, Phase One,
Reconyx, Ricoh, Samsung, Sanyo, Sigma/Foveon and Sony.

The R package **exiftoolr** provides a thin wrapper around ExifTool
and allows one to read image file metadata from one or more files into
a `data.frame` with a simple command:

```{r, eval=FALSE}
library(exiftoolr)
exif_read(path = c("my_file_1.jpg", "my_file_2.jpg"))
```

## Basic installation

To download and install **exiftoolr**, run the following:

```{r, eval=FALSE}
if(!require(devtools)) {install.packages("devtools")}
devtools::install_github("JoshOBrien/exiftoolr")
```

Before using the package, you will need to have a working local copy
of ExifTool installed on your computer.  Because **exiftoolr** does
not ship with an included copy of ExifTool you will likely want to run
the following (just once following package installation) to download
and install the latest version of ExifTool into your local
**exiftoolr** package directory:

```{r, eval=FALSE}
library(exiftoolr)
install_exiftool()
```

Finally, to check that ExifTool has been properly installed, run:

```{r, eval=FALSE}
exif_version()
```
	   

## More installation details

[ExifTool][exiftool-home] is written and primarily distributed as Perl
library that relies on a working local installation of Perl. Perl is
present on most *NIX and Mac machines, but is not by default installed
on Windows machines. Fortunately, for Windows users, Phil Harvey
distributes a stand-alone ExifTool executable that does not require
Perl. (Windows users who do have Perl installed (from, for example,
[Strawberry Perl][Strawberry]) may of course alternatively use the
Perl library).

Depending on one's operating system, running `install_exiftool()` will
install either the ExifTool Perl library (on *NIX and Mac machines) or
a stand-alone executable that works without a local Perl installation
(on Windows machines). For more details, see the `install_exiftool`
help page.



[exiftool-home]: http://www.sno.phy.queensu.ca/%7Ephil/exiftool/
[Strawberry]: http://www.strawberryperl.com/
